A Closer Look at Network Flow on Evolving Graphs

### 2018-05-14 paper.tex
finish katz centrality example

\begin{lstlisting}
function temporal_katz(g::AbstractEvolvingGraph,
  start::TimeNode; alpha = 0.1, max_level = 5)
    score = 0.
    v = start
    fronter = [v]
    level = 0
    while level < max_level
        next = []
        for u in fronter
            for v in forward_neighbors(g, u)
                push!(next, v)
                td = temporal_distance(start, u)
                d = td + level
                score += alpha^d
            end
        end
        fronter = next
        level += 1
    end
    return score
end
\end{lstlisting}

% explain the code
The algorithm \texttt{temporal\_katz} performs breadth first search (BFS) starting at \texttt{TimeNode} $v$, which represent a node at a specific time stamp \footnote{See also \url{https://etymoio.github.io/EvolvingGraphs.jl/latest/base.html#EvolvingGraphs.TimeNode}}.
For each \texttt{TimeNode} $v$, we accumulate the influence of linked nodes according to their spatial and temporal
distance from $v$. The spatial distance is recorded in variable \texttt{level} and the temporal distance is calculated by
\texttt{temporal\_distance}. The algorithm stops searching when \texttt{level} is larger or equal to \texttt{max\_level}.

% example on 3 timestamp evolving graph
For Figure \ref{}

% compare the Katz in EvolvingGraphs.jl

>>>>

\begin{lstlisting}
function temporal_katz(g::AbstractEvolvingGraph,
  start::TimeNode; alpha = 0.2, max_level = 10)
    score = 0.
    v = start
    fronter = [v]
    level = 0
    while level < max_level
        next = []
        for u in fronter
            for v in forward_neighbors(g, u)
                push!(next, v)
                td = temporal_distance(start, u)
                d = td + level
                score += alpha^d
            end
        end
        fronter = next
        level += 1
    end
    return score
end
\end{lstlisting}

% explain the code
The algorithm \texttt{temporal\_katz} performs breadth first search (BFS) starting at \texttt{TimeNode} $v$, which represent a node at a specific time stamp \footnote{See also \url{https://etymoio.github.io/EvolvingGraphs.jl/latest/base.html#EvolvingGraphs.TimeNode}}.
For each \texttt{TimeNode} $v$, we accumulate the influence of linked nodes according to their spatial and temporal
distance from $v$. The spatial distance is recorded in variable \texttt{level} and the temporal distance is calculated by
\texttt{temporal\_distance}. The algorithm stops searching when \texttt{level} is larger or equal to \texttt{max\_level}.
We set \texttt{alpha} to be $0.2$ and \texttt{max\_level} to be $10$. Then
% example on 3 timestamp evolving graph
for Figure \ref{fig:katz_eg2}, we have
\begin{lstlisting}
Dict{Any,Any} with 7 entries:
  TimeNode(B, 2) => 1.0
  TimeNode(B, 3) => 0.0
  TimeNode(A, 2) => 3.58333
  TimeNode(C, 1) => 1.06867
  TimeNode(A, 3) => 1.0
  TimeNode(B, 1) => 3.25373
  TimeNode(C, 2) => 1.71667
\end{lstlisting}
The total scores at all time stamps are
\begin{lstlisting}
DataStructures.DefaultDict{Any,Any,Float64} with 3 entries:
  "B" => 4.25373
  "A" => 4.58333
  "C" => 2.78533
\end{lstlisting}
Notice that $A$ is still the most important node in the network. However, now $B$ is considered more important
than $C$. This is because we consider causal edges as well as static edges. Node $B$ is active at all three time stamps
and more connected causally than node $C$.

For Figure \ref{fig:katz_eg3}, we have
\begin{lstlisting}
Dict{Any,Any} with 7 entries:
  TimeNode(C, 1)   => 1.06833
  TimeNode(B, 100) => 0.0
  TimeNode(C, 2)   => 1.70833
  TimeNode(B, 2)   => 1.0
  TimeNode(B, 1)   => 3.25367
  TimeNode(A, 100) => 1.0
  TimeNode(A, 2)   => 3.54167
\end{lstlisting}
The sum of node scores at each time stamp is
\begin{lstlisting}
DataStructures.DefaultDict{Any,Any,Float64} with 3 entries:
  "B" => 4.25367
  "A" => 4.54167
  "C" => 2.77667
\end{lstlisting}
We see the scores of all three nodes are decreased when the last time stamp is $100$.
Node $A$ is affected the most.
